\documentclass[a4paper]{article}

\usepackage{fontawesome}
\usepackage[margin=1cm]{geometry}
\usepackage{helvet}
\usepackage[bookmarks=false,colorlinks=true]{hyperref}
\usepackage{titlesec}
\usepackage{titling}

\pagenumbering{gobble}

\author{Tom Bell}

\renewcommand{\familydefault}{\sfdefault}

\renewcommand{\maketitle}{
  \begin{center}
    \huge{\textbf\theauthor}
  \end{center}
}

\newcommand{\datedsubsection}[2]{
  \subsubsection{#1 \hfill \textbf{#2}}
}

\newcommand{\languagetag}[1]{
  \raisebox{0.3\height}{\tiny #1}
}

\titleformat{\section}
{\large\uppercase}
{}
{0cm}
{\textbf}

\titleformat{\subsection}[runin]
{}
{}
{0cm}
{\textbf}[ --]

\titleformat{\subsubsection}
{}
{}
{0cm}
{}

\titleformat{\paragraph}
{}
{}
{0cm}
{}

\begin{document}

\maketitle

\begin{center}
  \raisebox{0\height}{\small\faMapMarker} Manchester, UK
  \hspace{1cm}
  \raisebox{-0.1\height}{\small\faMobile} +447478713163
  \hspace{1cm}
  \raisebox{-0.1\height}{\small\faEnvelope} tomb@tomb.io
  \hspace{1cm}
  \raisebox{-0.1\height}{\small\faGithubAlt} github.com/tombell
\end{center}

\section{Introduction}
\paragraph{I've been writing code since the late 90's, where I wrote BASIC from
magazines onto a Commodore 64 with an uncle. Since then I've always been
interested in programming and building cool projects. I've picked up numerous
programming languages over the years from C/C++, to PHP/Ruby, to modern
JavaScript/TypeScript and Go, with many others in between.}

\paragraph{I value clean code that is easy to pick up and understand, especially
for people new to a code base. This includes making sure things such as prettier
and eslint are setup to ensure the quality and consistency of code.}

\paragraph{I've worked on desktop apps, mobile apps, distributed apps, and
server side apps. Professionally the last few years I have settled on being a
full-stack developer utilising modern JavaScript/TypeScript on the front-end.
Outside of work, I've developed a numer of productivity tools for macOS, for
myself.}

\section{Experience}

\datedsubsection{\textbf{Residently} -- Senior Software Engineer}{2019 -- Present}
\begin{itemize}
  \item Developed and deployed various Ruby on Rails API apps for different
    stages of renting from the application process to contract generation.
  \item Started Next based React apps for resident and partner facing apps
    communicating with our APIs via JSON API.
  \item Worked on the mobile app built with React-Native for residents, and
    testing with Detox.
  \item Created a system that handles incoming emails, and support messages from
    residents in the mobile app, so everything is routed and grouped
    conversationally correctly.
  \item Added and maintained linting (ESLint/Rubocop) and formatting
    (Prettier) workflow in our Ruby and JavaScript/TypeScript apps.
  \item Created a system for \textit{conventions} whereby engineers could
    document our preferred ways of building and testing things, such as service
    objects, mocking in tests, and performing code reviews.
  \item Mentored junior engineers with topics including Ruby, Rails, RSpec,
    TypeScript, Jest, and refactoring.
\end{itemize}

\datedsubsection{\textbf{Capsule} -- Software Developer}{2012 -- 2019}
\begin{itemize}
  \item \textbf{Capsule Mobile} -- built using Cordova, Backbone, and
    CoffeeScript (eventually converted to ES6 JavaScript). The app used the
    public API to synchronise data, and store it (Web SQL) so the app could work
    offline, and then reconcile the offline data with online data.
  \item \textbf{Capsule for Gmail} -- built using JavaScript and the Gmail
    add-on SDK. This made CRM  data available inside emails within Gmail, and
    gave the ability to store the emails in the CRM, and access to other CRM
    features.
  \item \textbf{Capsule Connector for Google Data Studio} -- built using
    JavaScript and the data studio SDK, the connector allows Google Data Studio
    to pull in CRM data, which allows users to create dashboard and other data
    visualisations.
  \item Built internal dashboards, monitoring, and CI/CD tools.
\end{itemize}

\section{Technical Skills}

\subsection{Languages}
\textit{JavaScript, TypeScript, Go, Ruby, Swift, Lua}

\subsection{Environments}
\textit{Web (React, vanilla JS), Node (Next, vanilla), Ruby (Rails, Sinatra),
Databases (PostgreSQL, Redis), iOS (React-Native, Cordova), macOS (App, CLI),
Hosting (AWS, Heroku)}

\subsection{Other}
\textit{Linux/UNIX (Bash/ZSH, SSH, administration), Docker, Git, GitHub
(Actions), GitLab (CI/CD workflows), SQL, Testing}

\section{Education}

\datedsubsection{\textbf{Software Engineering} -- University of Central
Lancashire}{2006 -- 2009}
\textit{Diploma of Higher Education - Software Engineering}

\datedsubsection{\textbf{Access to Higher Education} -- Boston College}{2005 --
2006}
\textit{Business, Computing, Mathematics}

\section{Hobbies}
\paragraph{My main hobby at the minute is DJing. I first learnt to DJ back in
2018 and have been honing and learning new skills consistently. I often perform
a 1 to 2 hour mix weekly live on \href{https://twitch.tv/iamdjriff}{Twitch}.}

\paragraph{I've built and maintained several side projects. A typical side
project for me is something that helps increase productivity.}

\begin{itemize}
  \item \href{https://github.com/starkwm/stark}{Stark} \languagetag{(Swift)}
    Window manager powered by JavaScript for macOS
  \item \href{https://github.com/starkwm/skbd}{skbd} \languagetag{(Swift)}
    Daemon for binding shell commands to shortcut keys for macOS
  \item \href{https://github.com/tombell/memoir}{Memoir API} \languagetag{(Go)}
    \href{https://github.com/tombell/memoir-app}{Memoir App}
    \languagetag{(TypeScript, Preact)} Web app for sharing tracklists for my DJ
    mixes
  \item \href{https://github.com/tombell/legend}{Legend} \languagetag{(Go,
    TypeScript, Preact)} API service and web overlay for OBS for displaying the
    currently playing track(s) in Rekordbox
  \item \href{https://github.com/tombell/ensong}{Ensong} \languagetag{(Go)}
    Deamon that watches a directory for a WAV file, converts to AIFF and MP3 to
    backup and upload to Mixcloud
  \item \href{https://github.com/belt-project/belt.sh}{belt.sh}
    \languagetag{(Bash)} Set of bash scripts for performing devops tasks such as
    provisioning and deploying
\end{itemize}

\paragraph{I also like to play \href{https://magic.wizards.com/en}{Magic: the
Gathering} for fun, and have previously played at a competitive level.}

\end{document}
