\maketitle

\begin{center}
    \contactitem{0\height}{\faMapMarker}{Manchester, United Kingdom}
    \hspace{1 cm}
    \contactitem{-0.1\height}{\faEnvelope}{tomb@tombell.dev}
    \hspace{1 cm}
    \contactitem{-0.1\height}{\faGithubAlt}{github.com/tombell}
\end{center}

\section{Introduction}
\paragraph{I've been coding since the late 90s starting with BASIC on a Commodore 64. From then, I've been passionate about programming and have learned several languages from Ruby, Go, to modern JavaScript/TypeScript. Also dabbling with Swift for personal projects.}

\paragraph{I've gained experience developing desktop, mobile, distributed, and web applications. As a full-stack developer, I specialize in TypeScript for front end development, and Ruby/Go for the back-end. Beyond my professional work, I've also created several productivity tools for macOS, and related to my hobby as a DJ.}

\section{Experience}

\datedsubsection{\textbf{Residently} Senior Software Engineer}{Aug 2019---Mar 2026}
\begin{itemize}
    \item Built the integrations feature for building integrations with third party systems.
    \item Developed and deployed multiple Ruby on Rails API apps for various stages of the rental process.
    \item Started resident and partner facing dashbaords built with Next.js using the internal JSON:API.
    \item Contributed to React-Native mobile app development for a resident focused app.
    \item Established a system for documenting our engineering conventions, covering things from building, testing, service objects, mocking, and code reviews.
    \item Implemented a system for processing incoming and outgoing emails for residents implementing our customer support channel in our mobile app.
    \item Provided mentoring to junior engineers on topics such as Ruby, Rails, RSpec, TypeScript, Jest, and refactoring.
    \item Collaborated closely with our product managers and designers.
\end{itemize}

\datedsubsection{\textbf{Capsule} Software Developer}{Jan 2012---Aug 2019}
\begin{itemize}
    \item \textbf{Capsule Mobile:} Developed using Cordova, Backbone, and CoffeeScript. This app utilized a public API to synchronize and store data offline (Web SQL), later reconciling it with online data.
    \item \textbf{Capsule for Gmail:} Created using JavaScript and the Gmail add-on SDK, enabling CRM data integration within Gmail emails. Users could store emails in the CRM and access additional CRM features.
    \item \textbf{Capsule Connector for Google Data Studio:} Developed with JavaScript and the Data Studio SDK, enabling Google Data Studio to pull in CRM data for creating dashboards and visualizations.
    \item Built internal dashboards, monitoring tools, and CI/CD pipelines.
\end{itemize}

\section{Skills}

\subsection{Languages:} JavaScript, TypeScript, Go, Ruby, Swift, Lua, and some other languages.

\subsection{Environments:} React/Preact, Node/Bun, Ruby (Rails), Databases (PostgreSQL, Redis), iOS (React Native), macOS (App, CLI), Hosting (AWS, Digital Ocean, Heroku)

\subsection{Other:} Linux (Shell, SSH, administration), Docker, Git, GitHub (Actions), GitLab (CI/CD workflows), SQL, Testing

\section{Education}

\datedsubsection{\textbf{Software Engineering} University of Central Lancashire}{2006---2009}
\textit{Diploma of Higher Education Software Engineering}

\datedsubsection{\textbf{Access to Higher Education} Boston College}{2005---2006}
\textit{Business, Computing, Mathematics}

\section{Hobbies}
\paragraph{My main hobby is DJing. I began DJing in 2018 and continue to refine my skills, often performing live streams once or twice a month on Twitch. I also enjoy playing board games/tabletop games, attending a weekly board games night with friends.}

\paragraph{Typically I use side projects as a way to keep up my skills and learn new technologies and techniques. My favourite side projects are my productivity boosting tools like Stark and skbd.}

\begin{itemize}
    \item \href{https://github.com/starkwm/stark}{stark}: macOS window manager powered by JavaScript. \textit{Swift}
    \item \href{https://github.com/starkwm/skbd}{skbd}: macOS daemon that binds shell commands to shortcut keys. \textit{Swift}
    \item \href{https://github.com/starkwm/saod}{saod}: macOS daemon that executes shell commands when output audio device changes \textit{Swift}
    \item \href{https://github.com/tombell/memoir}{Memoir}: Back end REST-like API for managing DJ mix tracklists. \textit{Go, PostgreSQL}
    \item \href{https://github.com/tombell/memoir-app}{Memoir App}: Web front end for the Memoir API. \textit{TypeScript, Preact, Zod, Nanostores}
    \item \href{https://github.com/tombell/ensong}{Ensong}: Daemon that monitors directories for WAV files, converting them to AIFF for backup and MP3 for upload to Mixcloud. \textit{Go, S3, GitHub}
    \item \href{https://github.com/belt-project/belt.sh}{belt.sh}: A collection of bash scripts for various devops tasks such as provisioning and deployment. \textit{Bash, Ubuntu}
\end{itemize}
